---
title: "2_explore"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
 
# Import library

```{r}

rm (list = ls())

# Helper
library (tidyverse)

# Import
library (rio)

# Exploration 
library (DataExplorer)
library (janitor)
library (arsenal)
library (ggforce)
library (gganimate)

# functional plots and outliers
library (rainbow)
library (mrfDepth)

# modelling
library (FDboost)

# parallel
library(doParallel)
library(foreach)
library (furrr)

# custom 

source ("code/helper_fun.R")

```

# Import raw data

```{r}

output_dir <- "output"

list_of_files <- list.files(output_dir, pattern = ".RDS")
incl_studies <- c("fukuchi|taylor|horst|lencioni|schreiber")

list_of_files <- list_of_files[grepl (incl_studies, list_of_files)]

df.list <- list()

for (n in seq_along(list_of_files)) {
  
  
  df.list[[n]] <- readRDS (file.path(output_dir, list_of_files[n]))
  
}

names (df.list) <- str_remove (list_of_files, ".RDS")


```

# Clean data

## lencioni data

```{r}

temp <- df.list$df_lencioni %>%
  map (~.$biomech) %>%
  bind_rows() %>%
  separate(task, into = c("task", "rep"), sep = "_")%>%
  mutate_if (is.character, ~tolower(.)) %>%
  mutate (task = str_trim (task),
          var_axis = str_trim (var_axis),
          val = ifelse (side == "lx" & var_axis == "ankleadd", val * -1, 
                        ifelse (task %in% c("toewalking", "walking") & side == "lx" & var_axis == "anklerot", val * -1, val))) %>%
  filter (var_axis %in% c("anklepwr", "kneepwr", "hippwr")) %>%
  filter (task == "walking") %>%
  mutate (study = "lencioni",
          joint = ifelse (var_axis == "anklepwr", "ankle",
                          ifelse (var_axis == "kneepwr", "knee",
                                  "hip"))) %>%
  arrange (subj, speed) %>%
  group_by(subj)  %>%
  group_split () %>%
  map (select_middle) %>%
  bind_rows() %>%
  ungroup () %>%
  dplyr::select (-c(task, strlen, strwid, cadence, var_axis))


```


## Individual plot
 
```{r}

df_plot <- temp %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "lencioni" 

fig_name <- "individual_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Save back to df.list

```{r}
df.list$df_lencioni <- temp
```


## taylor data

```{r}

temp <- df.list$df_taylor %>%
  mutate (study = "taylor") %>%
  dplyr::select (-c(cadence, strlen)) %>%
  mutate (var = str_remove (var, "Pow")) %>%
  mutate_if (is.character, ~tolower(.)) %>%
  rename (joint = var)

```


## Individual plot
 
```{r}

df_plot <- temp 

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = as.factor (subj))) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "taylor" 

fig_name <- "individual_plot.pdf"


pdf (width = 10, height = 6, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()



```

## Remove outlier

```{r}
temp2 <- temp %>%
  pivot_wider(names_from = "cycle",
              values_from = "val")



for (n in seq_along(unique (temp2$joint))) {
  
  var <- unique (temp2$joint)[n]
  
  temp2 [temp2$joint == var, names (temp2) %in% c(1:101)] <- 
    my_outlier(temp2 [temp2$joint == var, names (temp2) %in% c(1:101)])
  
  
  
}

temp3 <- temp2 %>%
  na.omit() %>%
  pivot_longer(cols = c(`1`:`101`),
               names_to = "cycle",
               # names_ptypes = list (cycle = numeric()),
               values_to = "val")

temp3$cycle <- parse_number(temp3$cycle)
```


## recheck individual plot
 
```{r}

df_plot <- temp3 

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "taylor" 

fig_name <- "individual_clean_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Save back to df.list

```{r}
df.list$df_taylor <- temp3
```


## horst data

```{r}

temp <- df.list$df_horst %>%
  mutate (study = "horst") %>%
  rename (val = pwr,
          rep = reps) %>%
  mutate (val = val/wt) 

```


## Individual plot
 
```{r}

df_plot <- temp %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "horst" 

fig_name <- "individual_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Remove outlier

```{r}
temp2 <- temp %>%
  pivot_wider(names_from = "cycle",
              values_from = "val")



for (n in seq_along(unique (temp2$joint))) {
  
  var <- unique (temp2$joint)[n]
  
  temp2 [temp2$joint == var, names (temp2) %in% c(1:101)] <- 
    my_outlier(temp2 [temp2$joint == var, names (temp2) %in% c(1:101)])
  
  
  
}

temp3 <- temp2 %>%
  na.omit() %>%
  pivot_longer(cols = c("1":"101"),
               names_to = "cycle",
               # names_ptypes = list (cycle = numeric()),
               values_to = "val")
temp3$cycle <- parse_number(temp3$cycle)
```


## recheck individual plot
 
```{r}

df_plot <- temp3 %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "horst" 

fig_name <- "individual_clean_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Save back to df.list

```{r}
df.list$df_horst <- temp3
```

## schreiber data

```{r}

temp <- df.list$df_schreiber %>%
  mutate (study = "schreiber") %>%
  rename (val = pwr,
          rep = reps) %>%
  mutate (val = val/wt) %>%
  mutate (sex = ifelse (sex == 0, "f", "m")) %>%
  na.omit() 

```


## Individual plot
 
```{r}

df_plot <- temp %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "schreiber" 

fig_name <- "individual_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Remove outlier

```{r}
temp2 <- temp %>%
  pivot_wider(names_from = "cycle",
              values_from = "val") %>%
  na.omit()



for (n in seq_along(unique (temp2$joint))) {
  
  var <- unique (temp2$joint)[n]
  
  temp2 [temp2$joint == var, names (temp2) %in% c(1:101)] <- 
    my_outlier(temp2 [temp2$joint == var, names (temp2) %in% c(1:101)])
  
  
  
}

temp3 <- temp2 %>%
  na.omit() %>%
  pivot_longer(cols = c("1":"101"),
               names_to = "cycle",
               # names_ptypes = list (cycle = numeric()),
               values_to = "val")
temp3$cycle <- parse_number(temp3$cycle)

temp3 <- temp3 %>%
  group_by(subj, study, side, joint, age, ht, wt, sex, cycle) %>%
  summarise(val = mean (val, na.rm = TRUE),
            speed = mean (speed)) %>%
  ungroup ()

```


## recheck individual plot
 
```{r}

df_plot <- temp3 %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "schreiber" 

fig_name <- "individual_clean_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Save back to df.list

```{r}
df.list$df_schreiber <- temp3
```

## fukuchi data

```{r}

temp <- df.list$df_fukuchi %>%
  rename (val = pwr,
          rep = reps) %>%
  mutate (study = "fukuchi")%>%
  mutate (val = val/wt)


```


## Individual plot
 
```{r}

df_plot <- temp %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "fukuchi" 

fig_name <- "individual_plot.pdf"


pdf (width = 10, height = 6, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()



```


## Remove outlier

```{r}
temp2 <- temp %>%
  pivot_wider(names_from = "cycle",
              values_from = "val") %>%
  na.omit ()

for (n in seq_along(unique (temp2$joint))) {
  
  var <- unique (temp2$joint)[n]
  
  temp2 [temp2$joint == var, names (temp2) %in% c(1:101)] <- 
    my_outlier(temp2 [temp2$joint == var, names (temp2) %in% c(1:101)])
  
  
  
}

temp3 <- temp2 %>%
  na.omit() %>%
  pivot_longer(cols = c("1":"101"),
               names_to = "cycle",
               # names_ptypes = list (cycle = numeric()),
               values_to = "val")
temp3$cycle <- parse_number(temp3$cycle)
```


## recheck individual plot
 
```{r}

df_plot <- temp3 %>%
  unite ("subj_rep_side", subj, rep, side, sep = "_")

  
f <- ggplot (data= df_plot) +
  geom_line (aes (x = cycle, y = val, colour = subj_rep_side)) +
  facet_wrap( ~ joint) + 
  theme(legend.position = "none")

data_name <- "fukuchi" 

fig_name <- "individual_clean_plot.pdf"


pdf (width = 10, height = 8, file = file.path(output_dir, paste0 (data_name, "_", fig_name)))
f
dev.off()


```

## Save back to df.list

```{r}
df.list$df_fukuchi<- temp3
```


# Combine five data

## Average over subj

```{r}
df.list2 <- list()
for (n in seq_along(df.list)) {
  
  df.list2[[n]] <- df.list[[n]] %>%
    group_by(study, 
             subj, 
             age, 
             sex, 
             wt, 
             ht, 
             speed, 
             joint, 
             cycle) %>%
    summarise(val = mean (val, na.rm = TRUE)) %>%
    ungroup ()
  
  
}

```

## Change subj names

```{r}

for (n in seq_along(df.list2)) {
  
  df.list2[[n]] <- df.list2[[n]] %>%
    mutate (subj = paste0(study, "_", subj))
  
}

```

## Bind df.list

```{r}
df <- df.list2 %>%
  bind_rows() %>%
  mutate (sex = str_trim(sex))
```

## Plot of power over cycle, age, speed

```{r}

age_cut <- seq (5, 95, 10)
age_labels <- paste0 (paste (age_cut, "-", age_cut[-1])[-length (age_cut)], " (yo)")

speed_cut <- seq (0.5, 2.0, 0.5)
speed_labels <- paste (speed_cut, "-", speed_cut[-1])[-length (speed_cut)]

df_plot <- df %>%
  mutate (age_cat  = cut (age, age_cut, labels = age_labels),
          speed_cat  = cut (speed, speed_cut, labels = speed_labels)) %>%
  group_by(speed_cat, age_cat, joint, cycle) %>%
  summarize (val = mean(val, na.rm = TRUE)) %>%
  ungroup ()



f <- ggplot (data = df_plot) +
  geom_line (aes (x = cycle, y = val, colour = speed_cat)) +
  guides(colour = guide_legend(title="Speed (m/s)")) +
  facet_wrap_paginate(age_cat~joint, ncol = 3, nrow = 2, page = 3)

n <- n_pages(f)

fig_name <- "summary_plots.pdf"

pdf (width = 10, height = 8, file = file.path(output_dir, fig_name))

for (i in 1:n) {
  
  print (f + facet_wrap_paginate(age_cat ~ joint, ncol = 3, nrow = 2, page = i))
  
}

dev.off()

```

# Explore distributions

## Power against cycle

```{r}


fig_name <- "explore_power_cycle.tiff"


tiff (width = 10, height = 8, units = "in", res = 200, file = file.path(output_dir,  fig_name))

df %>%
  ggplot () +
  geom_point (aes (x = cycle, y = val)) +
  facet_wrap( ~ joint)

dev.off()

```

## Power against age

```{r}

fig_name <- "explore_power_age.tiff"


tiff (width = 10, height = 8, units = "in", res = 200, file = file.path(output_dir,  fig_name))

df %>%
  ggplot () +
  geom_point (aes (x = age, y = val)) +
  facet_wrap( ~ joint)

dev.off()

```

## Power against Speed

```{r}

fig_name <- "explore_power_speed.tiff"


tiff (width = 10, height = 8, units = "in", res = 200, file = file.path(output_dir,  fig_name))

df %>%
  ggplot () +
  geom_point (aes (x = speed, y = val)) +
  facet_wrap( ~ joint)

dev.off()

```

## Histogram of power

```{r}

fig_name <- "explore_power_hist.tiff"


tiff (width = 10, height = 8, units = "in", res = 200, file = file.path(output_dir,  fig_name))

df %>%
  ggplot () +
  geom_density (aes (val), adjust = 10) +
  facet_wrap( ~ joint)

dev.off()

```

## Boxplot power against sex

```{r}

fig_name <- "explore_power_sex.tiff"


tiff (width = 10, height = 8, units = "in", res = 200, file = file.path(output_dir,  fig_name))

df %>%
  ggplot () +
  geom_boxplot(aes (x = sex, y = val)) +
  facet_wrap( ~ joint)

dev.off()


```

## Skewness

### By cycle

```{r}
df %>%
  group_by(joint, cycle) %>%
  summarise(val = skewness (val)) %>%
  ggplot () +
  geom_line (aes (x = cycle, y = val )) +
  facet_wrap(~ joint, ncol = 3) +
  geom_hline (yintercept = 0)
```

### By  age

```{r}
df %>%
  group_by(joint, age) %>%
  summarise(val = skewness (val)) %>%
  ggplot () +
  geom_line (aes (x = age, y = val )) +
  facet_wrap(~ joint, ncol = 3) +
  geom_hline (yintercept = 0)

```

### By speed

```{r}
df %>%
  group_by(joint, speed) %>%
  summarise(val = skewness (val)) %>%
  ggplot () +
  geom_line (aes (x = speed, y = val )) +
  facet_wrap(~ joint, ncol = 3) +
  geom_hline (yintercept = 0)

```

## Kurtosis

### By cycle

```{r}
df %>%
  group_by(joint, cycle) %>%
  summarise(val = kurtosis (val)) %>%
  ggplot () +
  geom_line (aes (x = cycle, y = val )) +
  facet_wrap(~ joint, ncol = 3) +
  geom_hline (yintercept = 3)
```

### By age

```{r}
df %>%
  group_by(joint, age) %>%
  summarise(val = kurtosis (val)) %>%
  ggplot () +
  geom_line (aes (x = age, y = val )) +
  facet_wrap(~ joint, ncol = 3) +
  geom_hline (yintercept = 3)

```

### By speed

```{r}
df %>%
  group_by(joint, speed) %>%
  summarise(val = kurtosis (val)) %>%
  ggplot () +
  geom_line (aes (x = speed, y = val )) +
  facet_wrap(~ joint, ncol = 3) +
  geom_hline (yintercept = 3)

```

# Export data
 
```{r}

output_dir <- "output"
file_name <- "df_clean.RDS"

saveRDS(df, file = file.path(output_dir, file_name))

```
